An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-14 EconGrowth-R-Functions.Rnw
Added the ability of CIvsParamPlot to use the CES model without energy and retrofitted the presentation to handle this correctly.

#      CES: gamma, lambda, delta_1, sigma_1, delta, or sigma

@@

  else if (model == "CES"){data <- cesParamsTableDF(energyType)}

>>>>

#      CES: gamma, lambda, delta_1, sigma_1, or delta
#     CESe: gamma, lambda, delta_1, sigma_1, delta, or sigma

@@

  else if (model == "CES"){data <- cesParamsTableDF(energyType=NA)}
  else if (model == "CESe"){data <- cesParamsTableDF(energyType)}

### 2013-04-14 EconGrowth.Rnw
Added the ability of CIvsParamPlot to use the CES model without energy and retrofitted the presentation to handle this correctly.

      \item AIC rows in the AIC table (Code is in the createAICTable function, but it is not yet working)

@@

\item Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command?

>>>>

      \item{AIC rows in the AIC table. Code is in the createAICTable function, but it is not yet working. Need to find a way to calculate AIC from the object that is returned from the cesEst function.}

@@

\item{Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command?}
\item{Heun: Add data from 2011 and, possibly, 2012 to the models}

### 2013-04-14 EconGrowthSeminar.Rnw
Added the ability of CIvsParamPlot to use the CES model without energy and retrofitted the presentation to handle this correctly.

\begin{frame}{$CI_{\delta}$ vs. $\delta$ for CES with $q$} %----------------------------
<<CI_delta_vs_delta_Graph_Q, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
CIvsParamPlot(model="CES", param="delta", energyType="Q")
@
\end{frame}

@@

\begin{frame}{$CI_{\delta}$ vs. $\delta$ for CES with $x$} %----------------------------
<<CI_delta_vs_delta_Graph_X, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
CIvsParamPlot(model="CES", param="delta", energyType="X")
@
\end{frame}

\begin{frame}{$CI_{\delta}$ vs. $\delta$ for CES with $u$} %----------------------------
<<CI_delta_vs_delta_Graph_U, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
CIvsParamPlot(model="CES", param="delta", energyType="U")
@
\end{frame}

@@

\begin{frame}{$CI_{\sigma}$ vs. $\sigma$ for CES with $q$} %----------------------------
<<CI_sigma_vs_sigma_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
CIvsParamPlot(model="CES", param="sigma", energyType="Q")
@
\end{frame}

>>>>

\begin{frame}{$CI_{\delta}$ vs. $\delta$ for CES with $q$} %----------------------------
<<CI_delta_vs_delta_Graph_Q, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
CIvsParamPlot(model="CESe", param="delta", energyType="Q")
@
\end{frame}

@@

\begin{frame}{$CI_{\delta}$ vs. $\delta$ for CES with $x$} %----------------------------
<<CI_delta_vs_delta_Graph_X, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
CIvsParamPlot(model="CESe", param="delta", energyType="X")
@
\end{frame}

\begin{frame}{$CI_{\delta}$ vs. $\delta$ for CES with $u$} %----------------------------
<<CI_delta_vs_delta_Graph_U, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
CIvsParamPlot(model="CESe", param="delta", energyType="U")
@
\end{frame}

@@

\begin{frame}{$CI_{\sigma}$ vs. $\sigma$ for CES with $q$} %----------------------------
<<CI_sigma_vs_sigma_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
CIvsParamPlot(model="CESe", param="sigma", energyType="Q")
@
\end{frame}
